Anonymizing ids

### 2024-06-22 src/count_completed.Rmd
Update 2018 files

```{r md_links}
c_text <- "page_update: "
f_text <- "[sim1]: "
md_files$page_update_line <- "999"
md_files$old_link <- "999"
for (i_row in 1:nrow(md_files)) {
  full_file_name <- glue("{md_path}/{md_files$yr[i_row]}/{md_files$fn[i_row]}")
  read_lines(full_file_name) -> file_text
  file_text %>%
    str_subset(fixed(c_text)) %>%
    str_replace(fixed(c_text), "") -> page_update
  file_text %>%
    str_subset(fixed(f_text)) %>%
    str_replace(f_text, "") %>%
    paste0("") %>%
    paste0(collapse=", ") -> old_link
  n <- length(page_update)
  if (n > 1) {
    cat(
      glue(
        "\n\n{n} duplicates found in {full_file_name}.\n\n"))}
  page_update %>%
    paste0("", collapse=", ") -> md_files$page_update_line[i_row]
  md_files$old_link[i_row] <- old_link
}
count(md_files, page_update_line)
# count(md_files, yr, page_update_line)
```

>>>>

```{r md_links}
c_text <- "page_update: "
f_text <- "\[sim1\]\: "
md_files$page_update_line <- "999"
md_files$old_link <- "999"
for (i_row in 1:nrow(md_files)) {
  full_file_name <- glue("{md_path}/{md_files$yr[i_row]}/{md_files$fn[i_row]}")
  read_lines(full_file_name) -> file_text
  file_text %>%
    str_subset(fixed(c_text)) %>%
    str_replace(fixed(c_text), "") -> page_update
  file_text %>%
    str_subset(f_text) %>%
    str_replace(f_text, "") %>%
    paste0("", collapse=", ") -> old_link
  n <- length(page_update)
  if (n > 1) {
    cat(
      glue(
        "\n\n{n} duplicates found in {full_file_name}.\n\n"))}
  page_update %>%
    paste0("", collapse=", ") -> md_files$page_update_line[i_row]
  md_files$old_link[i_row] <- old_link
}
count(md_files, page_update_line)
# count(md_files, yr, page_update_line)
```

### 2024-06-22 text/21/anonymizing-ids.Rmd
Update 2018 files

---
title: "Anonymizing ids"
author: "Steve Simon"
source: new
date: "2021-06-10"
categories:
- Blog post
tags:
- Privacy in research
output: html_document
---

>>>>

---
title: "Anonymizing ids"
author: "Steve Simon"
source: new
date: "2021-06-10"
categories:
- Blog post
tags:
- Privacy in research
output: html_document
page_update: complete
---
